full title

### 2020-11-21 paper/pldi21/eval.tex
Minor fix

To experimentally evaluate the conjecture, we investigated the relationship between
the communication cost between analyzers and the number of dynamic shortcuts.
For 198 original tests, the communication cost was only
\inred{x.xx}\% of the total analysis time.  However, for 143
abstracted tests, the communication cost was 82.49\% of the
total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
analysis time ratio for 143 abstracted tests.
The $x$-axis represents the time ratio normalized by the total analysis time of
the baseline analysis (no-DS) and the $y$-axis denotes the number of dynamic
shortcuts and the number of corresponding tests.
For all 143 tests, the communication cost (Comm. Cost) is larger than
both the static analysis time (Static) and the dynamic analysis
time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
the communication cost is modest compared with the baseline static
analysis time.  However, the more dynamic shortcuts are performed,
the less the performance benefits by using sealed symbolic execution.
Specifically, when dynamic shortcuts are performed more than
20 times, DS-Comm. is even larger than no-DS.
Based on this evaluation result, we believe that we can leverage
dynamic shortcuts by optimizing the communication between static and dynamic analyzers.

>>>>

To experimentally evaluate the conjecture, we investigated the relationship between
the communication cost between analyzers and the number of dynamic shortcuts.
For 198 original tests, the communication cost was only
3.51\% compared to the analysis time without dynamic shortcuts (no-DS).  However, for 143
abstracted tests, the communication cost was 82.49\% compared to the analysis
time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
analysis time ratio for 143 abstracted tests.
The $x$-axis represents the time ratio normalized by the total analysis time of
the baseline analysis (no-DS) and the $y$-axis denotes the number of dynamic
shortcuts and the number of corresponding tests.
For all 143 tests, the communication cost (Comm. Cost) is larger than
both the static analysis time (Static) and the dynamic analysis
time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
the communication cost is modest compared with the baseline static
analysis time.  However, the more dynamic shortcuts are performed,
the less the performance benefits by using sealed symbolic execution.
Specifically, when dynamic shortcuts are performed more than
20 times, DS-Comm. is even larger than no-DS.
Based on this evaluation result, we believe that we can leverage
dynamic shortcuts by optimizing the communication between static and dynamic analyzers.
